Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-22 paper/paper.tex
Deleting minor results and emphasizing 3 major ones

@@

\section{Additional results (most likely should be deleted)}

\begin{observation}
    The lower bound of $\Omega(\ell)$ holds even with $1/3-1/k$-augmentation, i.e., in scenarios where the capacity of each cluster of the algorithm is $(1+1/3)\cdot k - 1$, while the capacity of OPT's clusters is $k$.
    To this end we use the construction from Observation~\ref{obs:lb_general_k}.
    We observe that each cluster of the algorithm can fit exactly $3$ components of size $k/3$.

    \maciek{This refers to simpler proof with $k=3$}
  \end{observation}

    \maciek{Note that this does not contradict the existence of $O((1+1/\epsilon)\cdot k \cdot \log(k))$ algorithm of Avin, Bienkowski et al, as the algorithm requires $2+\epsilon$-augmentation.}

    \subsection{On a Cost of a Single Repartition}

    \subsubsection{A Costly Repartition Example}

    A repartition cost is bounded by $O(kl)$ (cite marcin-chen).
    Now we show that the rebalance may be expensive (cubic) in terms of $k$, even for $l$ linear in $k$.

    This justifies taking a different approach to repartitioning then bounding the repartition cost in $O(k^2\cdot \ell^2)$ algorithm (described in Section ``A simple upper bound'' in the DISC paper).
    As the cost of a specific repartition is $\Omega(k^2)$, then the cost of DET during a single phase is: for each of $O(k \cdot l)$ edges revealed, we already have the cost $O(k^2)$ (precisely, $O(min\{k^2, k\ell\})$, and the competitive ratio would be $O(k^3\cdot \ell)$. \maciek{This would be an improvement in terms of $\ell$ still, but no hopes for $O(k\ell)$ algorithm just by improving the rebalancing analysis}

    \maciek{Possibly simplify $\Omega(k^3)$? Or just present $\Omega(k^2)$?}

    \subsubsection{For Constant k, Repartition Cost is Constant?}

    \maciek{Interesting research problem: is a single repartition cost bounded by $O(poly(k))$? This would improve currently best-known $O(k^2\ell^2)$ to $O(k\cdot poly(k) \cdot \ell)$, i.e., would tighten the lower bound in terms of $\ell$.}
      \maciek{We have such examples for $k=3,4,5$. It gives us an $O(\ell)$-competitive algorithm for $k=3$}

    \begin{theorem}
      There exists a $O(\ell)$-competitive algorithm for $k=3$.
    \mahmoud{is this needed anymore?}
    \maciek{It does not overlap with any other result from this paper.}
    \end{theorem}

          \subsection{$O(k)$-competitive algorithm for the ring}

          \maciek{todo}

          We know that the lower bound is $k$ for the ring communication pattern (cite Marcin-Chen).
          The simple matching (assymptotically \maciek{maybe it is easy to have $k$ exactly?}) upper bound is to fix the reconfiguration to be the cyclic shift. We reconfigure upon encountering inter-cluster request. We use phases: upon discovering the edge on each cut we charge OPT 1 and reset counters.

>>>>

\section{$O(\ell)$-competitive algorithm for $k=3$}

\begin{theorem}
  There exists a $O(\ell)$-competitive algorithm for $k=3$.
\end{theorem}

@@
